### 2022-11-07 README.Rmd
div
Link to OSF audio
Updated README
Big rename of 5 functions

`onsetsync` is a R package for musical assessing synchrony between onsets in music. <img src="man/figures/logo.png" align="right" height="139"/> There are functions for common operations such as adding isochronous beats based on metrical structure, adding annotations, calculating classic measures of synchrony between performers, and assessing periodicity of the onsets, and visualising synchrony across cycles, time, or another property.

@@

@@

```{r paired1}
set.seed(1234) # set random seed
N <- 200 # Let's select 200 onsets
Bootstrap <- 1000
d1 <- sync_sample_paired(CSS_Song2,'Clave','Bass',N,Bootstrap,'SD',TRUE)
print(paste('Mean asynchrony of',round(mean(d1$asynch*1000),1),
    'ms & standard deviation of',round(sd(d1$asynch*1000),1),'ms'))
```
There are other measures to summarise the asynchronies and visualise them.

### Calculate synchrony across performances

We can apply the measures to a corpus of performances. Here we load five Cuban Son and Salsa performances and run the same analysis as above across the performances.

```{r corpus, warning=FALSE, message=FALSE, eval=TRUE,fig.width=6.0}
corpus <- onsetsync::CSS_IEMP
D <- sync_sample_paired(corpus,'Tres','Bass',N=0,beat='SD')
D <- D$asynch
D$asynch_abs <- abs(D$asynch)*1000
fig3 <- plot_by_dataset(D,'asynch_abs','name', box = TRUE)
print(fig3)
```

For more examples, see [documentation](https://tuomaseerola.github.io/onsetsync/) and associated [paper IN PROGRESS](http://).

#### Note: How do I get onsets from my music?

Note that `onsetsync` is not dedicated to extraction of onsets from audio as that should be done using other tools (e.g. [Librosa](https://librosa.org), or [MIR Toolbox for Matlab](https://www.jyu.fi/hytk/fi/laitokset/mutku/en/research/materials/mirtoolbox), or [Sonic Visualiser](https://www.sonicvisualiser.org) using established onset detection algorithms). Here we assume that you have extracted the onsets of the music from a recording already in one of these tools, and preferably checked them by hand. It is already more meaningful to carry out analyses of synchrony when you have the metrical information (cycles and beats) identified. If your starting point is MIDI, getting the onsets is just a conversion operation away (I would recommend [music21](https://web.mit.edu/music21/doc/moduleReference/moduleConverter.html) for this purpose), although annotation might still be required.

>>>>

`onsetsync` is a R package for musical assessing synchrony between onsets in music. There are functions for common operations such as adding isochronous beats based on metrical structure, adding annotations, calculating classic measures of synchrony between performers, and assessing periodicity of the onsets, and visualising synchrony across cycles, time, or another property.

@@

Go and <A HREF="https://osf.io/z9uxs/" target="_blank">listen to the song at OSF</A>.

@@

```{r paired1}
set.seed(1234) # set random seed
N <- 200 # Let's select 200 onsets
Bootstrap <- 1000
d1 <- sync_sample_paired(CSS_Song2,'Clave','Bass',N,Bootstrap,'SD',TRUE)
print(paste('Mean asynchrony of',round(mean(d1$asynch*1000),1),
    'ms & standard deviation of',round(sd(d1$asynch*1000),1),'ms'))
```

There are other measures to summarise the asynchronies and visualise them.

For more examples, see [Get started](docs/articles/onsetsync.html).
